{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-13 paper/paper.tex
added commata
corrected wording

Further there is a relation $\mapsto$ that describes possible successor
instructions. \texttt{exit} is the only instructions with no successor
and \texttt{start \textit{pc}} may only have a single successor (the
following program point).

>>>>

Further, there is a relation $\mapsto$ that describes possible successor
instructions. \texttt{exit} is the only program point with no successor
and \texttt{start \textit{pc}} may only have a single successor (the
following program point).
